04-Data-Analysis

### 2021-04-20 00-Data-Processing/04-Data-Analysis.Rmd

```{r}
access_by_da <- accessibility %>%
  st_drop_geometry() %>%
  # Copy the DA identifier to the accessibility table
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              transmute(UID = ID, DAUID),
            by = "UID") %>%
  # Group by DA and time
  group_by(DAUID, timing) %>%
  # Calculate the accessibility by DA before and during covid
  summarize(accessibility = sum(accessibility),
            timing = first(timing),
            .groups = "drop") %>%
  # Pivot wider to calculate the differences in accessibility from pre-covid to covid
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` / `Pre-covid` - 1) %>%
  # Join DA geometry
  left_join(data_da_2016 %>%
            transmute(DAUID = GeoUID,
                      geometry),
          by = "DAUID") %>%
  # Convert to simple features
  st_as_sf() 
tmap_mode("view")
tm_shape(access_by_da) + 
  tm_fill("acc_d")
```

>>>>

Let's do some view maps to see if the results make sense
```{r message = FALSE}
access_by_da <- accessibility %>%
  st_drop_geometry() %>%
  # Copy the DA identifier to the accessibility table
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              transmute(UID = ID, DAUID),
            by = "UID") %>%
  # Group by DA and time
  group_by(DAUID, timing) %>%
  # Calculate the accessibility by DA before and during covid
  summarize(accessibility = sum(accessibility),
            timing = first(timing),
            .groups = "drop") %>%
  # Pivot wider to calculate the differences in accessibility from pre-covid to covid
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` / `Pre-covid` - 1) %>%
  # Join DA geometry
  left_join(data_da_2016 %>%
            transmute(DAUID = GeoUID,
                      geometry),
          by = "DAUID") %>%

  # Convert to simple features
  st_as_sf() 
tmap_mode("view")
tm_shape(access_by_da) + 
  tm_fill("acc_d") +
  tm_shape(foodbank_locations) + 
  tm_dots("COVIDClose")

d_access_by_taz <- accessibility %>%
  st_drop_geometry() %>%
  # Copy the DA identifier to the accessibility table
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              transmute(UID = ID, TAZUID),
            by = "UID") %>%
  # Group by DA and time
  group_by(TAZUID, timing) %>%
  # Calculate the accessibility by DA before and during covid
  summarize(accessibility = sum(accessibility),
            timing = first(timing),
            .groups = "drop") %>%
  # Pivot wider to calculate the differences in accessibility from pre-covid to covid
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_d = `During covid` / `Pre-covid` - 1) %>%
  # join taz geometry
  left_join(tts_taz %>%
            transmute(TAZUID = gta06,
                      geometry),
          by = "TAZUID") %>%

  # Convert to simple features
  st_as_sf()

tm_shape(d_access_by_taz) + 
  tm_fill("acc_d") + 
  tm_shape(foodbank_locations) + 
  tm_dots("COVIDClose")

access_by_taz <- accessibility %>%
  st_drop_geometry() %>%
  # Copy the DA identifier to the accessibility table
  left_join(dwelling_network_points_2016 %>%
              st_drop_geometry() %>%
              transmute(UID = ID, TAZUID),
            by = "UID") %>%
  # Group by DA and time
  group_by(TAZUID, timing) %>%
  # Calculate the accessibility by DA before and during covid
  summarize(accessibility = sum(accessibility),
            timing = first(timing),
            .groups = "drop") %>%
  # Pivot wider to calculate the differences in accessibility from pre-covid to covid
  pivot_wider(names_from = timing, 
              values_from = accessibility) %>%
  # Calculate changes in accessibility
  mutate(acc_pre = `Pre-covid`) %>%
  # join taz geometry
  left_join(tts_taz %>%
            transmute(TAZUID = gta06,
                      geometry),
          by = "TAZUID") %>%

  # Convert to simple features
  st_as_sf()

tm_shape(access_by_taz) + 
  tm_fill("acc_pre") + 
  tm_shape(foodbank_locations) + 
  tm_dots("COVIDClose")
